### 2016-06-29 publications/Journal/4a-allocation.tex
Add another missing reference
Fixed missing references

\subsection{Performance Evaluation}
%TODO do basic performance evaluation of allocation
%TODO show model in statistics view
In order to evaluate the influence of model allocation, we define a new model, based on PHOLD~\cite{PHOLD}.
The model structure resembles a tree: an atomic model can have a set of children, with children being connected to each other as well.
Connections can be uni- or bidirectional.

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtree_sequential_dn.eps}
    \caption{Effect of hierarchy in sequential simulation.}
    \label{fig:PHoldtree_seq_dn_benchmark}
\end{figure}

@@

With breadth-first allocation, we traverse the tree in a breadth-first way, allocating subsequently visited atomic models to the same node.
This means, intuitively, that atomic models at the same level in the tree, but not necessarily siblings, are frequently allocated to the same node.
Since there is only infrequently some communication between 
This allocation strategy is shown in Figure~\ref{fig:BF}.

With depth-first allocation, we traverse the tree in a depth-first way, allocating subsequently visited atomic models to the same node.
This means, intuitively, that subtreees are frequently allocated to the same node.
This allocation strategy is shown in Figure~\ref{fig:DF}.

The breadth first allocation scheme will result in kernels that will form a dependency chain with multiple branches, much like in the Queue model.
Such a linear dependency chain can result in a parallel speedup as we demonstrated with the Queue model, but this is not always true as we will demonstrate in this section.
A single kernel that has an unbalanced number of atomic models or unequal computation load in transition functions will slow down the remainder of the chain. This effect is also apparent if the thread a kernel runs on is not fairly scheduled. In conservative this will lead to excessive polling of the other kernels' eot values, in optimistic this will lead to a cascade of reverts since dependent kernels will simulate ahead of the slower kernel. In Figures \ref{fig:pholdtree_visualize_parBFS} and \ref{fig:pholdtree_visualize_parDFS} the simulation trace is visualized for both allocation schemes highlighting the remarks made in this paragraph.
\begin{figure}
   \center

>>>>

\subsection{Performance Evaluation}
In order to evaluate the influence of model allocation, we define a new model, based on PHOLD~\cite{PHOLD}.
The model structure resembles a tree: an atomic model can have a set of children, with children being connected to each other as well.
Connections can be uni- or bidirectional.

@@

\begin{figure}
    \center
    \includegraphics[width=\columnwidth]{fig/pholdtree_sequential_dn.eps}
    \caption{Effect of hierarchy in sequential simulation.}
    \label{fig:PHOLDtree_seq_dn_benchmark}
\end{figure}

@@

With breadth-first allocation, we traverse the tree in a breadth-first way, allocating subsequently visited atomic models to the same node.
This means, intuitively, that atomic models at the same level in the tree, but not necessarily siblings, are frequently allocated to the same node.
Since there is only infrequently some communication between siblings, and even never between different subtrees, this does not sound an intuitive allocation.
This allocation strategy is shown in Figure~\ref{fig:PholdTree_model_bfs}.

With depth-first allocation, we traverse the tree in a depth-first way, allocating subsequently visited atomic models to the same node.
This means, intuitively, that subtreees are frequently allocated to the same node.
This allocation strategy is shown in Figure~\ref{fig:PholdTree_model_dfs}.

The breadth first allocation scheme will result in kernels that will form a dependency chain with multiple branches, much like in the Queue model.
Such a linear dependency chain can result in a parallel speedup as we demonstrated with the Queue model, but this is not always true as we will demonstrate in this section.
A single kernel that has an unbalanced number of atomic models or unequal computation load in transition functions will slow down the remainder of the chain.
This effect is also apparent if the thread a kernel runs on is not fairly scheduled.
In conservative this will lead to excessive polling of the other kernels' EOT values, in optimistic this will lead to a cascade of reverts since dependent kernels will simulate ahead of the slower kernel.
In Figure~\ref{fig:pholdtree_visualize_parBFS} and Figure~\ref{fig:pholdtree_visualize_parDFS} the simulation trace is visualized for breadth-first and depth-first, respectively, highlighting the remarks made in this paragraph.

\begin{figure}
   \center
